|

### 2019-07-16 inst/manuscript/manuscript.Rmd
Regenerate supplement files

# cluster 5 has too many proteins to fit in table
# but GO enrichment still possible
f5_clust5 <- f5_clusters %>% 
  filter(cluster == 5) %>% 
  mutate(id = gsub("RPS1", "CaO19.3002", id)) %>% 
  pull(id) %>% 
  stringr::str_extract_all(., "[^;]+") %>% 
  unlist() %>% 
  unique()

@@

# cluster 6 is proteins that could not be clustered
# because all 4 log2FCs = NA
f5_clust8 <- sort(rownames(f5_table_excl))

@@

f5_go3 <- process_fungifun("figures/f5_GO_clust3.csv") %>% 
  mutate(Prot.found = gsub("CaO19.4937", "CHS3", Prot.found))

# issue with CHS3, ambiguous ID in FungiFun, used CaO19.4937 as identifier
f5_go4 <- process_fungifun("figures/f5_GO_clust4.csv")

# issue with ALA1, MDH1, used CaO19.5746 and CaO19.7481 as identifiers
f5_go5 <- process_fungifun("figures/f5_GO_clust5.csv") %>% 
  mutate(Prot.found = gsub("CaO19.3002", "RPS1", Prot.found))

f5_go6 <- process_fungifun("figures/f5_GO_clust6.csv") %>% 
  mutate(Prot.found = gsub("CaO19.5746", "ALA1", Prot.found), 
         Prot.found = gsub("CaO19.7481", "MDH1", Prot.found), 
         Prot.found = gsub("CaO19.7417", "TSA1", Prot.found))

>>>>

f5_clust5 <- f5_clusters %>% 
  filter(cluster == 5) %>% 
  mutate(id = gsub("RPS1", "CaO19.3002", id)) %>% 
  pull(id) %>% 
  stringr::str_extract_all(., "[^;]+") %>% 
  unlist() %>% 
  unique()

@@

# cluster 8 is proteins that could not be clustered
# because all 4 log2FCs = NA
f5_clust8 <- sort(rownames(f5_table_excl))

@@

# issue with CHS3, ambiguous ID in FungiFun, used CaO19.4937 as identifier
f5_go3 <- process_fungifun("figures/f5_GO_clust3.csv") %>% 
  mutate(Prot.found = gsub("CaO19.4937", "CHS3", Prot.found))

f5_go4 <- process_fungifun("figures/f5_GO_clust4.csv")

# issue with RPS1, ambiguous ID in FungiFun, used CaO19.3002 as identifier
f5_go5 <- process_fungifun("figures/f5_GO_clust5.csv") %>% 
  mutate(Prot.found = gsub("CaO19.3002", "RPS1", Prot.found))

# issue with ALA1, MDH1, TSA1
# used CaO19.5746, CaO19.7481, CaO19.7417 as identifiers
f5_go6 <- process_fungifun("figures/f5_GO_clust6.csv") %>% 
  mutate(Prot.found = gsub("CaO19.5746", "ALA1", Prot.found), 
         Prot.found = gsub("CaO19.7481", "MDH1", Prot.found), 
         Prot.found = gsub("CaO19.7417", "TSA1", Prot.found))
